Structured Versus Decorated Cospans

### 2022-04-05 cospans_compositionality_3.tex
Added links for bib refs [32] and [39]

\bibitem{KSW} P.\ Katis, N.\ Sabadini and R.\ F.\ C.\ Walters, On the algebra of systems with feedback and boundary, \textsl{Rendiconti del Circolo Matematico di Palermo Serie II} \textbf{63} (2000), 123--156.

@@

\bibitem{Peterson} J.\ L.\ Peterson, \textit{Petri Net Theory and the Modeling of Systems}, Prentice-Hall, New Jersey, 1981.

>>>>

\bibitem{KSW} P.\ Katis, N.\ Sabadini and R.\ F.\ C.\ Walters, On the algebra of systems with feedback and boundary, \textsl{Rendiconti del Circolo Matematico di Palermo Serie II} \textbf{63} (2000), 123--156. Available at \href{https://citeseerx.ist.psu.edu/viewdoc/download?doi=10.1.1.51.5758&rep=rep1&type=pdf}{https://citeseerx.ist.psu.edu/viewdoc/download?doi=10.1.1.51.5758\&rep=rep1\&type=pdf}.

@@

\bibitem{Peterson} J.\ L.\ Peterson, \textit{Petri Net Theory and the Modeling of Systems}, Prentice-Hall, New Jersey, 1981. Available at \href{http://dl.icdst.org/pdfs/files3/2bf95f7fde49a09814231bbcbe592526.pdf}{http://dl.icdst.org/pdfs/files3/2bf95f7fde49a09814231bbcbe592526.pdf}.
